Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-11-01 Paper.tex
Last minute errata
One more last minute errata
Add files via upload

\begin{center}
  \includegraphics[keepaspectratio, width=0.2\textwidth]{images/lafonera-sourcewikipedia.eps}
  \\
  Figure 1. \textit{La Fonera's initial project router.}
\end{center}

@@

% \begin{tabular} to 0.5\textwidth { | X[l] | X[r] | }
\begin{tabular}{ | m{0.125\textwidth} | m{0.3125\textwidth} | }
 \hline
 Specs & Raspberry Pi 3 Model B \\
 \hline
 CPU & Broadcom BCM2837, Cortex-A53 (ARMv8) 64-bit SoC @ 1,2 GHz \\
\hline
 RAM & 1 GB \\
\hline
 Connectivity & Wi-Fi 802.11 b/g/n (2,4 GHz) Bluetooth 4.1 Ethernet card up to 100 Mbps \\
\hline
 Ports & Full HDMI, 4 USB 2.0, MicroSD, CSI camera, DSI display \\
\hline
 Memory & MicroSD \\
\hline
\end{tabular}
\end{center}
\vspace{0.15cm}
Table 1. Raspberry Pi 3 Model B specs

@@

Both Mythrill and Manticore have reported a low severity warning located on function
\textit{claimTimeOut}, due to the use of the special variable \textit{block.timestamp}, -refered
to as \textit{now}.

@@

Mythrill also reports this low severity warning located on function \textit{closeChannel}:

@@

Recommendations for further study as well as all of the source code generated in the project are also provided.
\newline\newline
Source code published in GitHub (public software repository) under MIT license:
\newline\newline
\href{https://github.com/ethereum-internet-access}{https://github.com/ethereum-internet-access}
\newline\newline
A demo video subtitled is available at the following address on YouTube:
\newline\newline
\href{https://www.youtube.com/watch?v=C9pVMn-pu_8&hd=1}{YouTube video demo}

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/maxresdefault.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 10. A demo video screenshot.
\\
\end{center}
\vspace{0.15cm}
Finally, the following address on Etherscan shows the Ethereum transactions done:
\newline\newline

>>>>

\begin{center}
  \includegraphics[keepaspectratio, width=0.2\textwidth]{images/lafonera-sourcewikipedia.eps}
  \\
  Figure 1. \textit{La Fonera's initial project router\cite{fon}.}
\end{center}

@@

% \begin{tabular} to 0.5\textwidth { | X[l] | X[r] | }
\begin{tabular}{ | m{0.125\textwidth} | m{0.3125\textwidth} | }
 \hline
 Specs & Raspberry Pi 3 Model B \\
 \hline
 CPU & Broadcom BCM2837, Cortex-A53 (ARMv8) 64-bit SoC @ 1.2 GHz \\
\hline
 RAM & 1 GB \\
\hline
 Connectivity & Wi-Fi 802.11 b/g/n (2.4 GHz) Bluetooth 4.1 Ethernet card up to 100 Mbps \\
\hline
 Ports & Full HDMI, 4 USB 2.0, MicroSD, CSI camera, DSI display \\
\hline
 Memory & MicroSD \\
\hline
\end{tabular}
\end{center}
\vspace{0.15cm}
Table 1. Raspberry Pi 3 Model B specs

@@

Both Mythril and Manticore have reported a low severity warning located on function
\textit{claimTimeOut}, due to the use of the special variable \textit{block.timestamp}, -refered
to as \textit{now}.

@@

Mythril also reports this low severity warning located on function \textit{closeChannel}:

@@

Recommendations for further study as well as all of the source code generated in the project are also provided.
\newline\newline
Source code published in GitHub (public software repository) under MIT license:
\newline\newline
\href{https://github.com/ethereum-internet-access}{https://github.com/ethereum-internet-access}
\newline\newline
A demo video subtitled is available at the following hyperlink to YouTube:
\newline\newline
\href{https://www.youtube.com/embed/C9pVMn-pu_8?rel=0&hl=en&cc_lang_pref=en&cc_load_policy=1}{YouTube video demo}

\begin{center}
%\begin{figure}[h]
%  \centering
  \includegraphics[keepaspectratio, width=0.5\textwidth]{images/maxresdefault.eps}
%  \caption{Figura 2. Raspberry Pi 3 Modelo B. Fuente: [Raspberry 18]}
%\end{figure}
\\
Figure 10. A demo video screenshot.
\\
\end{center}
\vspace{0.15cm}
Finally, the following hyperlinks to Etherscan show the Ethereum transactions done:
\newline\newline
